Results Coding

### 2023-12-22 analysis/practiceCoding_AW.Rmd
code cleaning and manuscript
removed irrelevant code from 'practiceCoding_AW'. Drafting up a manuscript for NHB as an .rmd file.

```{r}
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(kableExtra) # for tables
library(knitr) # for literate programming
library(janitor) # for data munging
library(tidylog) # for inline code feedback
library(here) # for finding files
library(validate) # for data validation and testing
#library(ggthemr) # for ggplot theme
library(ggrepel) # for ggplot text labels
library(scales) # to wrap text on axis labels
library(ggdist) # for plotting distributions
library(patchwork) # for multipanel plot layouts
library(ggbeeswarm) # for dotplots
```

@@

d_journals <- read_csv(here('data','processed','d_journals.csv'))
d_articles <- read_csv(here('data','processed','d_articles.csv'))

```
# Create separate tibbles for Prominent and Randomly-selected journal samples
```{r}
dj_prominent <- d_journals %>%
  filter(sample_id != "random") %>%
  filter(is_empirical == TRUE)

@@

# Calculate CIs for YES [**EDIT TO DERIVE NUMBERS FROM DATA**]
Not sure if this makes sense to do for Prominent and Total, as these are not random samples
```{r}
library(binom)

# Prominent Sample data
prominentSuccess <- 1
randomSuccess <- 23
totalSuccess <- 57

sample_size <- 100
totalSample <- 189
confidence_level <- 0.95

# Calculate the Wilson confidence interval
ci_prominent <- binom.confint(prominentSuccess, sample_size, method = "wilson", conf.level = confidence_level)
ci_random <- binom.confint(randomSuccess, sample_size, method = "wilson", conf.level = confidence_level)
ci_total <- binom.confint(totalSuccess, totalSample, method = "wilson", conf.level = confidence_level)

# Print the confidence interval
print(ci_prominent)
print(ci_random)
print(ci_total)
```

# Calculate CIs for NO [**EDIT TO DERIVE NUMBERS FROM DATA**]
```{r}
library(binom)

# Prominent Sample data
prominentNO <- 77
randomNO <- 74
totalNO <- 123

# Calculate the Wilson confidence interval
ci_prominentNO <- binom.confint(prominentNO, sample_size, method = "wilson", conf.level = confidence_level)
ci_randomNO <- binom.confint(randomNO, sample_size, method = "wilson", conf.level = confidence_level)
ci_totalNO <- binom.confint(totalNO, totalSample, method = "wilson", conf.level = confidence_level)

# Print the confidence interval
print(ci_prominentNO)
print(ci_randomNO)
print(ci_totalNO)
```

@@

# Filter and transform restrictions for ppc_length
ppc_length_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>% # removes Archive Only PPC types
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>% 
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and transform restrictions for ppc_time
ppc_time_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data <- bind_rows(
  ppc_length_data %>% mutate(Code = "Length"),
  ppc_time_data %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

@@

ggsave(filename = "Prominent_statements.png", plot = last_plot(), device = "png")
```
# Create and combine restiction statement graphs with ppc acceptance (random sample)
```{r}

# Filter and process data for ppc_length
ppc_length_random <- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and process data for ppc_time
ppc_time_random<- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data_random <- bind_rows(
  ppc_length_random %>% mutate(Code = "Length"),
  ppc_time_random %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(binom)
library(kableExtra) # for tables
library(knitr) # for literate programming
library(janitor) # for data munging
library(tidylog) # for inline code feedback
library(here) # for finding files
library(validate) # for data validation and testing
#library(ggthemr) # for ggplot theme
library(ggrepel) # for ggplot text labels
library(scales) # to wrap text on axis labels
library(ggdist) # for plotting distributions
library(patchwork) # for multipanel plot layouts
library(ggbeeswarm) # for dotplots
```

@@

d_articles <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique', 'data','processed','d_articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('ProjCode', 'GitClone', 'PROJ_2023_psych-journal-critique','data','processed','d_journals.csv'), show_col_types = F) # journal data 
```

# Create separate tibbles for Prominent and Randomly-selected journal samples
```{r}
dj_prominent <- d_journals %>%
  filter(sample_id != "random") %>%
  filter(is_empirical == TRUE)

@@

# Calculate CIs for YES [**EDIT TO DERIVE NUMBERS FROM DATA**]
Not sure if this makes sense to do for Prominent and Total, as these are not random samples
```{r}

# Prominent Sample data
prominentSuccess <- dj_prominent %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES") %>%
  count()
randomSuccess <- dj_random %>%
  filter(ppc_type == "A") %>%
  filter(has_ppc == "YES") %>%
  count()

sample_size <- 100
confidence_level <- 0.95

# Calculate the Wilson confidence interval
ci_prominent <- binom.confint(prominentSuccess, sample_size, method = "wilson", conf.level = confidence_level)
ci_random <- binom.confint(randomSuccess, sample_size, method = "wilson", conf.level = confidence_level)

# Print the confidence interval
print(ci_prominent)
print(ci_random)
```

@@

# Filter and transform restrictions for ppc_length
prominent_length_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>% # removes Archive Only PPC types
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all length limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>% 
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and transform restrictions for ppc_time
prominent_time_data <- dj_prominent %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative' # Summarises all time limits as 'Quantitative', 'Qualitative', or 'Not Stated'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data <- bind_rows(
  prominent_length_data %>% mutate(Code = "Length"),
  prominent_time_data %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

@@

ggsave(filename = "Prominent_statements.png", plot = last_plot(), device = "png")
```

```{r}
# Load the dplyr package
library(dplyr)

# Calculate the count and percentage for "Quantitative"
quantitative_data <- prominent_length_data %>%
 filter(ppc_length == "Quantitative") %>%
 summarise(count = sum(count), percentage = sum(count) / sum(prominent_length_data$count) * 100)

# Print the count and percentage for "Quantitative"
print(paste(quantitative_data$count, "(", round(quantitative_data$percentage, 2), "%)", sep = ""))

# Create and combine restiction statement graphs with ppc acceptance (random sample)
```{r}

# Filter and process data for ppc_length
random_length_data <- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and process data for ppc_time
random_time_data <- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data_random <- bind_rows(
  random_length_data %>% mutate(Code = "Length"),
  random_time_data %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))
